\chapter{E\_boresight\_calibration.py}\
\label{ch:scriptE}

\section{Purpose}
An interactive GUI application for visually determining the boresight rotation angles. It uses Open3D for 3D visualization and Tkinter for the control panel.

\section{Background}
The boresight calibration process involves adjusting three rotation angles (Roll/X, Pitch/Y, Yaw/Z) until the point cloud appears geometrically correct. The tool applies the rigid body transformation in real time as sliders are moved.

\section{Input File Requirements}
\begin{table}[h!]
    \centering
    \begin{tabular}{@{}lll@{}}
        \toprule
        File        & Format & Columns Required                         \\ \midrule
        Point Cloud & .csv   & \texttt{gps\_time, x, y, z}              \\
        Trajectory  & .txt   & \texttt{time, x, y, z, roll, pitch, yaw} \\ \bottomrule
    \end{tabular}
\end{table}

\section{Running the Script}
\begin{lstlisting}[language=bash]
python E-boresight_calibration.py
\end{lstlisting}
Two windows open simultaneously: \textbf{Boresight Calibration Controls} (Tkinter) and \textbf{Boresight Calibration Viewer} (Open3D).

\section{Workflow}
\begin{enumerate}
    \item Click "Point Cloud (.csv)" $\rightarrow$ select the downsampled file from Script C.
    \item Click "Trajectory (.txt)" $\rightarrow$ select the converted file from Script B.
    \item Click "Apply \& View" $\rightarrow$ loads files and shows initial point cloud.
    \item Adjust Roll (X), Pitch (Y), and Yaw (Z) sliders.
    \item Note final values for use in Script D.
\end{enumerate}

\section{Boresight Calibration Strategy}
\begin{itemize}
    \item Adjust \textbf{Yaw (Z)} first --- typically has the largest effect on in-plane rotation.
    \item Adjust \textbf{Pitch (Y)} next to correct for tilt along the direction of motion.
    \item Adjust \textbf{Roll (X)} for fine vertical tilt.
\end{itemize}

\section{Possible Errors}
\begin{table}[h!]
    \centering
    \begin{tabular}{@{}lll@{}}
        \toprule
        Error                           & Cause                 & Fix                                         \\ \midrule
        ValueError: missing 'gps\_time' & Wrong CSV header      & Regenerate CSV using Script C               \\
        Open3D window does not open     & Version mismatch      & Ensure \texttt{open3d==0.19.0} is installed \\
        Very slow slider response       & Point cloud too large & Use 1\% CSV instead of 10\%                 \\ \bottomrule
    \end{tabular}
\end{table}
